\subsection{STU (imaginable)}

At the Eindhoven University of Technology, the Student Service Centrum
(STU) is the department that registers new students.
This process starts when a new student makes an application request.
An administrative employee (AE) registers the request, and a mail department employee (MDE) sends an enrollment package to the student.
If the request is on time for the next academic year, this package contains two forms.
In case the request is late for the next academic year, the package contains the same two forms and a request for a motivation letter.
The first form asks for personal information, the study programs the student wishes to take, and financial details;
the second form asks whether the student wants to participate in the notebook project, and if so, more details about this participation.

If no answer is received within two weeks, the process ends without further message to the student.
Once the forms are received, an AE checks whether they are complete and puts them in the system.
If the forms are not complete, a new package is sent again by an MDE, with an explanation that something was missing.
If a motivation letter was required, it is sent back with the package.

Once all forms are complete, the Notebook Service Centrum (NSC) orders
a notebook, if the student opted to participate.
Meanwhile, STU processes the request further.
First, the prerequisites are checked.
Second, the financial details are checked by a financial department employee (FDE).
If these are not met, the student is notified and the process ends.
Third, if applicable, the motivation letter is checked by a departmental executive board employee (DEBE).
(If the DEBE rejects the motivation letter, the student is notified of this and the process stops.)
Fourth, the student is registered in the university by an AE of STU.
Fifth, the student is registered in the study programs by the departmental student administration
employee of the departments corresponding to the chosen study programs.
Finally, the student is notified of the successful registration.

Only if the request is not on time for the next academic year, NCS orders a separate notebook on receipt of the request.
Otherwise, the notebook is added to the bulk order for notebooks for the next academic year.
Once student registration cannot fail anymore and the notebook has arrived, payment is requested from the bank of the student.
In case the payment does not arrive before registration completes, the student has to pay at pick up.
In both cases, NSC notifies the student, who picks up the laptop and pays if necessary.

\clearpage
